

\begin{document}

In both the defense and retail fields, tracking the movement of people or groups of people is paramount. Whether it is to protect the perimeter of military installation, or to monitor the foot traffic through a grocery store isle, understanding the flow of people through an area is fundamental way of understanding a system. Being able to effectively detect, monitor, and measure the number of people crossing and do so a non intrusive manner is of extreme importance to both the military and retailers.

Literature review of both craftpersons websites and scientific journals have aided in the development of this IR transmitter application. Journal articles \cite{b1} and \cite{b2} demonstrate the feasibility for the tripwire in defense applications. One application was for the protection of defensive perimeters, while the other was a novel approach, using IR sensors to detect anti-personnel mines. Both are vital in the modern climate of war on terror, where reconstruction and defense of destabilized countries is the current modus operandi. Journal \cite{b3} establishes a body of work using the tripwire as a sensor to measure foot traffic. The measuring of foot traffic in retail can not be understated. This provides retailers with way of developing metrics to determine total foot traffic through any given part of a store. This would allow retailers to determine sales per aisle per person and be able determine the most cost effective way of product throughput.
	






\end{document}