\begin{document}
	
Ryan, Phil and Joseph have completed, at the time of this proposal, five semesters in the electical and computer engineering discipline. The most relevant skillsets for the purposes of this proposal is from the electronics course, ECE 342, which an optical uplink was simulated and designed by this team. This course focused primarily on microelecronic circuits and in-depth study of MOSFET's, BJT's and their implementation in circuits with operational amplifiers. 

Ryan is double majoring in Computer and Electrical engineering at the University of Maine. Relevant skills from coursework include Microcomputer Architecture and Design, ECE 473, which implements Verilog in design of Microprocessors, which is of use when designing hardware for the tripwire. Skills in microelectronics from Electronics I, ECE 342, is also of use for designing IR sensor circuits.

Phil is double majoring in Computer and Electrical engineering at the University of Maine. Relevant skills from coursework includes Sensor design, where the construction of sensors was outlined and  ECE 473, which implements Verilog in design of Microprocessors, which is of use when designing hardware for the tripwire. Skills in microelectronics from Electronics I, EC 342, is also of use for designing IR sensor circuits.

Joseph is an undergraduate majoring in electrical engineering at the University of Maine. Experience includes Electronics I, ECE 342, which is used in the development of the IR circuits used in this design as well as Signals and Systems, which provided the background in order to process the IR signal.
\end{document}